Molecular dynamics simulation of synchronization in driven particles

### 2021-02-04 manuscript/manuscript_ajp_2020.tex
updated figures and text

  Using reasonable values for the
  experimental analog of this system, 
  demonstrate the Reynolds number is low.
  In addition to the values listed in Table ~\ref{tab:1}, 
 % Approximate experimental values for
 % a colloid size and speed
 % are $D = 1 \mu m$ and $v \sim 1 \mu m /s$.
 % %Likewise
 % To first order the viscosity is $\eta \sim 10^{-3}$ Pa-s 
 % since 
 % viscosity of water decreases with temperature
 % from $1.3 \times 10^{-3}$ Pa-s at $10^{\circ}$ C to 
 % from $0.31 \times 10^{-3}$ Pa-s at $90^{\circ}$ C,
 % where 1 Pascal is $1$ N/m$^2$.
  %Likewise
  the liquid density $\rho$ varies with temperature
  with $\rho \sim 10^3$ kg/cm$^3$ a reasonable
  first order approximation
  \cite{asce}.

@@

  Newton's second law states that
  the acceleration of a particle $i$
  is proportional to 
  the sum of forces on the particle 
  \begin{equation}
  m_i \vec{a}_i = \sum \vec{F}_i
  \label{eq:n2l}
  \end{equation}
  where the constant of proportionality is the
  inertial mass $m_i$.  
  The addition of a dissipative force to a dynamical equation 
  of colloid motion 
  is typically modeled
  with a drag force proportional to the particle's velocity
  in the opposite direction of motion 
  $\vec{F}^{drag} = - \gamma \vec{v}_i$
  where $\gamma = 3 \pi \eta D$ is the drag coefficient
  described in Ex.~\ref{ex:reynolds}.
  The ratio of $m/\gamma$ is %has units of time, % and is 
  known as the momentum relaxation time, %.
  and is small for
  particles with low Reynolds numbers.
  The mass of the
  typical experimental colloid particle is $15$ picograms,
  leading to a momentum relaxation time
  % \tau = 15 nanograms/(3 pi D \eta)
  %$15*10^-12 / (3pi * 3*10^-6 meters * 0.001 Pa-s * 1000 g/kg)$  %1 Pa-s = 1 N s /m^2 = 1 kg /(m s)
  on the order of microseconds.
  %of $1.6 ~\mu$s.
  Confirm for the values listed in Table ~\ref{tab:1},
  the momentum relaxation time is 
  $m/\gamma \approx 0.5 ~\mu$s.

  When $m/\gamma$ is small,
  particle acceleration can be ignored
  entirely.
  (a) Using Newton's Second Law for
  a small momentum relaxation time, 
  demonstrate that a particle confined to a landscape exerting force
  $F^l(\vec{r}_i)$ subject to a time dependent drive $F^d(t)$
  can be modeled with the equation of motion described in 
  Eq.~\ref{eq:motion}.

@@

%\item
  \subsection{Integration Methods}
  \label{ex:euler}
  %{\it cut this one?  not really saying much}
    To calculate the position of the particle we
    integrate the equation of motion using
    the standard definition of velocity
    $\vec{v}_i = d\vec{r}_i/dt$ 
    via the 
    %In our model we use the
    Euler method. % to solve this equation.
    Our equation of motion provides
    a direct calculation for particle velocity,
    as demonstrated in Ex.~\ref{ex:n2l}.

  When solving ordinary differential equations,
  the Euler method is effective for solving linear equations
  of the form
  $dy/dt = f(t,y(t))$ with initial condition $y(t_0) = y_0$.
  The solution is calculated algorithmically
  by stepping in time through $n$ integer steps
  $t_n = t_0 + n \Delta t$.
  At each subsequent step the new
  value for $y$ is calculated as a map solution using
  discrete times 
  $y_{n+1} = y_n + f(t_n,y_n)$.
  The Euler method can be applied to non-linear
  equations effectively if the time step $\Delta t$
  is kept sufficiently small \cite{Newman}.
  In our simulations we use the timestep $\Delta t = 0.001$,
  but we find for a single particle
  we can just as easily used 
  %examine 
  %for
  timesteps $\Delta t = 0.01$ and $\Delta t = 0.1$
  over the same maximum time
  (i.e. decrease the overall simulation time and sampling rate)
  and reproduce the motions shown in Fig.~\ref{fig:0}(b).
  This is due to the linear nature of the solution
  for an isolated particle.
  Apply the Euler method to our equation
  of motion to solve for the analytic expression
  of position of a particle
  $y_n$ at the $nth$ timestep (i.e. Eq.~\ref{eq:euler}).
  %How to the motions of the particle compare when the timestep
  %becomes large?
  [UPDATE]
  Demonstrate the timestep
  of a single particle can be made large
  with no change to the overall physics.
  You will need to modify the maximum
  simulation time, and the frequency of data saved for plotting purposes.

@@

  Often molecular dynamics algorithms 
  are solved with higher order methods
  such as the Verlet method or Runge-Kutta methods.
  These methods include  higher order terms
  that provide accurate solutions for
  second order differential equations,
  i.e. $dy/dt = v$ and $dv/dt = f_2(y,t)$.
  %where $f_2(y,t)$ is a second derivative function.
  In Newton's second law $f_2$ would be proportional
  to the net force on a single particle.

  In our model 
  we do not integrate $f_2(y,t)$ since 
  $a = dv/dt = 0$,
  and thus rearrange $f_2(y,t)$ to solve directly for $v$,
  as described in Ex.~\ref{ex:n2l}.
  The Taylor expansion of the position function $y(t)$
  \begin{equation}
    y(t_n \pm \Delta t) = y(t_n) \pm \frac{dy}{dt} \Delta t + \frac{1}{2} \frac{d^2y}{dt^2} (\Delta t)^2 + \ldots
    %\pm O(\Delta t)^3 ... %\frac{1}{6} \frac{d^3y}{dt^3} (\Delta t)^3 + ...
  \end{equation}
  is exact at first order
  for the $n$-th time step.

  Demonstrate how the Verlet method
  simplifies to the Euler method when
  the particle acceleration $a=0$.

  %We invite interested students to repeat this
  %simulation for any initial particle position %of $y$
  %and a range of simulation constants
  %to demonstrate that synchronization in this model
  %does not depend on a particular set of conditions.
  %but is a direct consequence of the simplicity of the model.

%\item
  \subsection{Brownian motion}
  \label{ex:brownian}
  Brownian motion 
  is a temperature and viscosity dependent
  phenomena in which 
  visible particles change direction,
  apparently at random, 
  due to collisions with invisible fluid particles.
  The frequency of collisions depends on the properties of
  the suspending fluid.
  At higher temperatures
  the increased kinetic energy of particles
  makes collisions more likely, 
  as described by the Maxwell-Boltzmann distribution \cite{Einstein1905}.

  %Consider a non-zero temperature in the simulation.
  %in which particles will collide with invisible particles
  %making up the suspending fluid.
  In molecular dynamics simulations temperature effects
  can be modeled with randomized forces $f^T$
  to emulate the motion of particles undergoing Brownian motion.
  A random distribution of forces
  causes motion
  equally in all
  directions such that the force averaged over a finite time interval
  is zero
  \begin{equation}
    \langle f^T(t) \rangle = \frac{1}{N} \sum_n^N f^T_n = 0
  \end{equation}
  where $n$ is an integer indicating
  discrete simulation timesteps
  such that $t = N \Delta t$.
  Random distributions are not correlated 
  over the independent variable,
  for the independent variable to be time
  \begin{equation}
  \langle f^T(t) f^T(\tau)\rangle = 2 \eta k_B T \delta(t-\tau)
  \end{equation}
  for times $t$ and $\tau$,
  where $\delta(t-\tau)$ is the Dirac-delta function.
  Here the scaling factor energy of 
  $k_B T$ is
  derived from the Boltzmann constant $k_B$
  and temperature $T$ \cite{Allen2017}.
  A particle
  with energy $k_b T_{min} > U_0$ may 
  hop over landscape
  barriers.

  % (a) 
  In simulation we define our temperature parameter to
  $k_b T/E_0 \rightarrow T$
  since we set the constants to unity.
  In these units we can compare 
  simulation temperature directly
  to force 
  in order to estimate the degree of random fluctuation.
  For instance, 
  with
  no applied driving force,
  the minimum temperature required for a single particle
  to hop between minima in the potential landscape is
  $T_{min} > A_p$.
  Assuming a particle is confined to
  move along the $y-$direction,
  include Brownian motion 
  in the model,
  we find the crossover
  to a hopping regime at $T/A_p \approx 5.6$.
  %when
  We demonstrate this hopping
  pattern in 
  %Measure the position vs. time
  a non-driven colloid for $T/A_p = 4.0, 5.0, 6.0$.
  %and note  a particle will hop a barrier
  %for sufficiently high $T/A_p$ ratios.
  Reproduce these results.

  \begin{center}
    \begin{figure}[h!]
      \centering
      \includegraphics[width=\columnwidth]{{brownian_particle_dt0.1}.pdf}
      \caption{
        Motion of a particle undergoing Brownian motion
        on a washboard potential
        energy landscape.
        (a) $T/A_p = 4.0$ no hopping occurs.
        (b) $T/A_p = 5.0$ a single hop occurs at $t = 130000$
        (c) $T/A_p = 6.0$ many hops occur.
        Note the scale of the $y-$axis differs in each panel.
      }
      \label{fig:brownian}
    \end{figure}
  \end{center}
  In Fig.~\ref{fig:brownian}
  we show the position versus time of a particle
  confined to a sinusoidal landscape
  undergoing Brownian motion.
  We increase the temperature relative
  to the amplitude of the landscape
  troughs until the particle enters a hopping regime.
  In  Fig.~\ref{fig:brownian}(a)
  $T/A_p = 4.0$ and the particle executes a 
  random walk centered at the potential minima $y/\lambda = 10$.
  We ran many simulations and never observed a hop to another minima.
  In  Fig.~\ref{fig:brownian}(b)
  $T/A_p = 5.0$ where hops between
  potential minima are possible but not probable,
  a single hop occurs from
  $y/\lambda = 10$ to $y/\lambda = 11$ at
  $t \sim 13000 \tau$.
  In other simulations with identical parameters,
  we sometimes observed no hops or two hops between minima,
  as expected with random fluctuating systems.
  In  Fig.~\ref{fig:brownian}(c)
  $T/A_p = 6.0$ 
  we observe approximately 15 hops,
  indicating the random thermalized kicks are
  sufficiently large to make the particle perform
  a random walk of hops a top the substrate
  in addition to the small scale random walk executed
  by all particles in this section.

  A quantity of interest
  for a particle undergoing Brownian motion
  is the rate of displacement
  of the particle from its initial position 
  This is measured as mean square displacement
  as a function of time
  \begin{equation}
    \langle \Delta \vec{r}(t) ^2 \rangle = \langle (\vec{r}(t + t_0) - \vec{r}(t_0))^2\rangle 
  \end{equation}
  where $t_0$ is the initial time at
  initial position $\vec{r}(t_0)$.
  With no substrate, we would expect
  the root mean square displacement (RMSD)
  to be proportional to the elapsed time 
  \begin{equation}
    \sqrt {\langle \Delta \vec{r}(t) ^2 \rangle} \propto t.
  \end{equation}
  Confirm this result for $A_p = 0$.
  %[INSERT advice on length of time to run?]
  Measure the RMSD as a function of time
  of a non-driven colloid for $T/A_p = 4.0, 5.0$, and $6.0$,
  as shown in Fig.~\ref{fig:brownian}.
  Compare your result to the
  substrate free RMSD.
  %%[INSERT EXPECTED RESULTS.  presumbably for sufficiently large $T/A_p$ the result collapsed back to standard diffusion.]

  %(b)
  How does Brownian motion affect
  the formation of Shapiro steps?
  With driving force reproduce the paper figures...
  %%[there is no way I want to run this with python...]

@@

  A range of oscillation behaviors
  can be explored by varying the
  relative strength of the confining landscape
  and external driving force.
  For the single driven particle,
  the hopping patterns are typically characterized
  by $n_f$ the number of steps forward
  versus $n_b$ the number of steps backward within a single
  time period.
  The total displacement of $n_f - n_b$ integer steps of
  the substrate period $\lambda$ characterize
  the net hop length.  
  In Fig.~\ref{fig:0},
  in a single period 
  the particle moves forward through two minima, i.e. $n_f = 2$,
  and does not move backward a full minima ($n_b = 0$).  
  %such that the pattern
  %is characterized as $2(2,0)$.
  In order to achieve
  backwards hops,
  a particle must have a ratio of $F^{ac}/F^{dc} > 1$,
  and a difference $|F^{ac} - F^{dc}| > A_p$.
  %which can also produce large forward hops.
  %INSERT figure with a range of hopping patterns for a run
  The frequency must be sufficiently low so that
  the time interval in which the applied force is large
  is sustained so that a particle will
  traverse a substrate extrema.
  Experiments with single colloids \cite{Juniper2015} 
  show 
  hopping patterns with backward steps are more difficult
  to achieve than forward,
  with $n_f = 0$ to $6$ for $n_b = 0$,
  $n_f = 0$ to $5$ for $n_b = -1$,
  and
  $n_f = 2$ to $3$ for $n_b = -2$
  were realized 
  for a variety of applied forces parameters $F^{dc}$ and $F^{ac}$.

  In Fig.~\ref{fig:hops}
  we show the results for lowering the frequency
  of the system for our original parameters.
  For the parameters
  $F^{dc}=0.1$, $F^{ac}=0.05$, and $a_p = 0.1$,
  $n_b = 0$
  across a broad range of frequencies,
  and $n_f$ increases as frequency decreases.
  Low frequencies
  result in sustained positive or negative motion of a particle,
  where in Fig.~\ref{fig:hops}(e)
  the particle reaches the top edge of the system
  and wraps back to $y=0$.

  In Fig.~\ref{fig:hops_back}
  we show the results for increasing $F^{ac}$
  of the system for our original parameters.
  Here $n_b$ increases from $n_b = 0$ in (a) to

  \begin{center}
    \begin{figure}[h!]
      \centering
      \includegraphics[width=\columnwidth]{{parameters_fig5}.pdf}
      \caption{
        Motion of a particle with the same values of $F^{dc} = 0.1$ and $F^{ac} = 0.05$ as Fig.~\ref{fig:1} and decreasing frequency as marked.    
      }
      \label{fig:hops}
    \end{figure}
  \end{center}
  %In Fig.~\ref{fig:hops}

  \begin{center}
    \begin{figure}[h!]
      \centering
      \includegraphics[width=\columnwidth]{{parameters_fig6}.pdf}
      \caption{
        Motion of a particle with the same values of $F^{dc}$ and frequency as Fig.~\ref{fig:1} and increasing $F^{ac}$.
        (a) The particle moves forward six minima with no steps backward.
        (b) The particle moves forward eight minima with two steps backward.
        (c) The particle moves forward nine minima with four steps backward.
      }
      \label{fig:hops_back}
    \end{figure}
  \end{center}
  %In Fig.~\ref{fig:hops}

%\item Frenkel-Kontorova and competing length scales for low temperature systems where thermal fluctuations are negligible
%  \item The Fokker-Planck Equation
%  \item Aubrey-Kontorova + commensurability
%  \item nanotribology
 %   kink motion
 %   Vanossi et al J.Phys.: Condens. Matter 19 (2007)
  %\item

@@

>>>>

  {\bf Using reasonable values for the
  experimental analog of this system, 
  show that the Reynolds number is small.}
  In addition to the values listed in Table ~\ref{tab:1}, 
 % Approximate experimental values for
 % a colloid size and speed
 % are $D = 1 \mu m$ and $v \sim 1 \mu m /s$.
 % %Likewise
 % To first order the viscosity is $\eta \sim 10^{-3}$ Pa-s 
 % since 
 % viscosity of water decreases with temperature
 % from $1.3 \times 10^{-3}$ Pa-s at $10^{\circ}$ C to 
 % from $0.31 \times 10^{-3}$ Pa-s at $90^{\circ}$ C,
 % where 1 Pascal is $1$ N/m$^2$.
  %Likewise
  the liquid density $\rho$ varies with temperature
  with $\rho \sim 10^3$ kg/cm$^3$ a reasonable
  first order approximation
  \cite{asce}.

@@

  Newton's second law states that
  the acceleration of a particle $i$
  is proportional to 
  the sum of forces on the particle 
  \begin{equation}
  m_i \vec{a}_i = \sum \vec{F}_i
  \label{eq:n2l}
  \end{equation}
  where the constant of proportionality is the
  inertial mass $m_i$.  
  The addition of a dissipative force to a dynamical equation 
  of colloid motion 
  is typically modeled
  with a drag force proportional to the particle's velocity
  in the opposite direction of motion 
  $\vec{F}^{drag} = - \gamma \vec{v}_i$
  where $\gamma = 3 \pi \eta D$ is the drag coefficient
  described in Ex.~\ref{ex:reynolds}.
  The ratio of $m/\gamma$ is %has units of time, % and is 
  known as the momentum relaxation time, %.
  and is small for
  particles with low Reynolds numbers.
  The mass of the
  typical experimental colloid particle is $15$ picograms,
  leading to a momentum relaxation time
  % \tau = 15 nanograms/(3 pi D \eta)
  %$15*10^-12 / (3pi * 3*10^-6 meters * 0.001 Pa-s * 1000 g/kg)$  %1 Pa-s = 1 N s /m^2 = 1 kg /(m s)
  on the order of microseconds.
  %of $1.6 ~\mu$s.
  {\bf Confirm for the values listed in Table ~\ref{tab:1},
  the momentum relaxation time is 
  $m/\gamma \approx 0.5 ~\mu$s. }

  When $m/\gamma$ is small,
  particle acceleration can be ignored
  entirely.
  (a) Using Newton's Second Law for
  a small momentum relaxation time, 
  {\bf show that a particle confined to a landscape exerting force
  $F^l(\vec{r}_i)$ subject to a time dependent drive $F^d(t)$
  can be modeled with the equation of motion described in 
  Eq.~\ref{eq:motion}. }

@@

%\item
  \subsection{Integration Methods}
  \label{ex:euler}
  %{\it cut this one?  not really saying much}
    To calculate the position of the particle we
    integrate the equation of motion using
    the standard definition of velocity
    $\vec{v}_i = d\vec{r}_i/dt$ 
    via the 
    %In our model we use the
    Euler method. % to solve this equation.
    Our equation of motion provides
    a direct calculation for particle velocity,
    as demonstrated in Ex.~\ref{ex:n2l}.  
  When solving ordinary differential equations,
  the Euler method is effective for solving linear equations
  of the form
  $dy/dt = f(t,y(t))$ with initial condition $y(t_0) = y_0$.
  The solution is calculated algorithmically
  by stepping in time through $n$ integer steps
  $t_n = t_0 + n \Delta t$.
  At each subsequent step the new
  value for $y$ is calculated as a map solution using
  discrete times 
  $y_{n+1} = y_n + f(t_n,y_n)$.
    {\bf Apply the Euler method to our equation
  of motion to solve for the analytic expression
  of position of a particle
  $y_n$ at the $nth$ timestep (i.e. Eq.~\ref{eq:euler}).}

  The Euler method can be applied to non-linear
  equations effectively if the time step $\Delta t$
  is kept sufficiently small \cite{Newman}.
  In our simulations we use the timestep $\Delta t = 0.001$,
  but we find for a single particle
  we can just as easily used 
  %examine 
  %for
  timesteps $\Delta t = 0.01$ and $\Delta t = 0.1$
  over the same maximum time
  (i.e. decrease the overall simulation time and sampling rate)
  and reproduce the motions shown in Fig.~\ref{fig:0}(b).
  This is due to the linear nature of the solution
  for an isolated particle.
  %How to the motions of the particle compare when the timestep
  %becomes large?
  %[UPDATE]
  {\bf Demonstrate the simulation timestep 
  can be large
  with no change to the overall physics
  in the motion of a single particle.}
  You will need to modify the maximum
  simulation time, and the frequency of data saved for plotting purposes.

@@

  Often molecular dynamics algorithms 
  are solved with higher order methods
  such as the Verlet or Runge-Kutta methods.
  These methods include  higher order terms
  that provide accurate solutions for
  second order differential equations,
  i.e. $dy/dt = v$ and $dv/dt = f_2(y,t)$.
  %where $f_2(y,t)$ is a second derivative function.
  In Newton's second law $f_2$ would be proportional
  to the net force on a single particle.
  In our model 
  we do not integrate $f_2(y,t)$ since 
  $a = dv/dt = 0$,
  %and thus rearrange $f_2(y,t)$ to solve directly for $v$,
  as described in Ex.~\ref{ex:n2l}.
  %The Taylor expansion of the position function $y(t)$
  %\begin{equation}
  %  y(t_n \pm \Delta t) = y(t_n) \pm \frac{dy}{dt} \Delta t + \frac{1}{2} \frac{d^2y}{dt^2} (\Delta t)^2 + \ldots
    %\pm O(\Delta t)^3 ... %\frac{1}{6} \frac{d^3y}{dt^3} (\Delta t)^3 + ...
  %\end{equation}
  %is exact at first order
  %for the $n$-th time step.
  %Demonstrate how the Verlet method
  %simplifies to the Euler method when
  %the particle acceleration $a=0$.
  %We invite interested students to repeat this
  %simulation for any initial particle position %of $y$
  %and a range of simulation constants
  %to demonstrate that synchronization in this model
  %does not depend on a particular set of conditions.
  %but is a direct consequence of the simplicity of the model.
%\item
  \subsection{Brownian motion}
  \label{ex:brownian}
  Brownian motion is a phenomena in which 
  visible particles change direction,
  apparently at random, 
  due to collisions with invisible fluid particles.
  The rate of collisions depends on the temperature, viscosity
  amd density of 
  the suspending fluid.
  At higher temperatures
  the increased kinetic energy of particles
  makes collisions more likely, 
  as described by the Maxwell-Boltzmann distribution \cite{Einstein1905}.

  %Consider a non-zero temperature in the simulation.
  %in which particles will collide with invisible particles
  %making up the suspending fluid.
  In molecular dynamics simulations
  it is common to treat the 
  invisible fluid particles as a continuous substance
  to reduce computational expense.
  Temperature effects
  can be modeled by applying randomized forces $f^T$
  to the visible particles.
  %\footnote{%In our simulations %np.random.normal
  We use the normal distristribution from the NumPy random module
  to generate a series of $f^T_n$ values for
  each integer timestep $n$ \cite{numpy}.
  A normalized random distribution of forces
  causes fluctuations in %particles to emulate Brownian
  motion 
  equally in all
  directions such that the force $f^T$
  averaged over a finite time interval
  is zero.  In one dimension this is expressed as 
  \begin{equation}
    \langle f^T(t) \rangle = \frac{1}{N} \sum_n^N f^T_n = 0
  \end{equation}
  %where $n$ is an integer indicating
  %discrete simulation timesteps
  such that $t = N \Delta t$.
  Random normal distributions are not correlated 
  over the independent variable,
  for the independent variable to be time
  \begin{equation}
  \langle f^T(t) f^T(\tau)\rangle = 2 \eta k_B T \delta(t-\tau)
  \end{equation}
  for times $t$ and $\tau$,
  where $\delta(t-\tau)$ is the Dirac-delta function.
  Here the scaling factor energy of 
  $k_B T$ is
  derived from the Boltzmann constant $k_B$
  and temperature $T$ \cite{Allen2017}.
  A particle
  with sufficient energy $k_b T_{min}$ may 
  hop over landscape
  barriers.
  % (a) 
  In our simulations,
  we define temperature as 
  $k_b T/E_0 \rightarrow T$
  with constants set to unity
  to
  %In these units
  compare directly with force. 
  %in order to estimate the degree of random fluctuation.

  {\bf With no applied driving force,
    find 
  the minimum temperature required for a single particle
  to hop over maxima in the potential landscape.}
  %$T_{min} > A_p$.
  Assume the particle is confined to
  move along the $y-$direction,
  include Brownian motion 
  in the model.
  In Fig.~\ref{fig:brownian},
  we demonstrate the transition
  from pinned to hopping
  in 
  %Measure the position vs. time
  a non-driven colloid for $T/A_p = 4.0, 5.0, 6.0$.
  The crossover
  to a hopping regime occurs at $T/A_p \approx 5.6$.
  %Reproduce these results.  
  \begin{center}
    \begin{figure}[h!]
      \centering
      \includegraphics[width=\columnwidth]{{brownian_particle_dt0.1}.pdf}
      \caption{
        Motion of a particle undergoing Brownian motion
        on a washboard potential
        energy landscape.
        (a) $T/A_p = 4.0$ no hopping occurs.
        (b) $T/A_p = 5.0$ a single hop occurs at $t = 130000$
        across a distance of $\Delta y = 2 \lambda$.
        (c) $T/A_p = 6.0$ many hops occur.
        Note the scale of the $y-$axis differs in each panel
        and the time scale is
        much greater than in Fig.~\ref{fig:1}.
      }
      \label{fig:brownian}
    \end{figure}
  \end{center}
  In Fig.~\ref{fig:brownian}
  we show the position versus time of a particle
  confined to a sinusoidal landscape
  undergoing Brownian motion.
  We increase the temperature relative
  to the amplitude of the landscape
  troughs until the particle enters a hopping regime.
  In  Fig.~\ref{fig:brownian}(a)
  the temperature is $T/A_p = 4.0$.
  The particle executes a 
  random walk centered at the potential minima $y/\lambda = 10$.
  We ran many simulations and never observed a hop to another minima
  within this simulation time.  
  In  Fig.~\ref{fig:brownian}(b)
  $T/A_p = 5.0$ where hops between
  potential minima are possible but not probable,
  a single hop occurs from
  $y/\lambda = 10$ to $y/\lambda = 12$ at
  $t \sim 40000 \tau$ and 
  $y/\lambda = 10$ to $y/\lambda = 8$ at
  $t \sim 280000 \tau$.
  In other simulations with identical parameters,
  we sometimes observed no hops or two hops between minima,
  as expected with random fluctuating systems.
  In  Fig.~\ref{fig:brownian}(c)
  $T/A_p = 6.0$ 
  we observe many hops.
  The random thermalized kicks are
  sufficiently large to make the particle perform
  what appears to be 
  a random walk of hops atop the substrate.
  %in addition to the small scale random walk executed
  %by all particles in this section.

  %A quantity of interest
  %for a particle undergoing Brownian motion
  %is the rate of displacement
  %of the particle from its initial position 
  %This is measured as mean square displacement
  %as a function of time
  %\begin{equation}
  %  \langle \Delta \vec{r}(t) ^2 \rangle = \langle (\vec{r}(t + t_0) - \vec{r}(t_0))^2\rangle 
  %\end{equation}
  %where $t_0$ is the initial time at
  %initial position $\vec{r}(t_0)$.
  %With no substrate, we would expect
  %the root mean square displacement (RMSD)
  %to be proportional to the elapsed time 
  %\begin{equation}
  %  \sqrt {\langle \Delta \vec{r}(t) ^2 \rangle} \propto t.
  %\end{equation}
  %Confirm this result for $A_p = 0$.
  %%[INSERT advice on length of time to run?]
  %Measure the RMSD as a function of time
  %of a non-driven colloid for $T/A_p = 4.0, 5.0$, and $6.0$,
  %as shown in Fig.~\ref{fig:brownian}.
  %Compare your result to the
  %substrate free RMSD.
  %%[INSERT EXPECTED RESULTS.  presumbably for sufficiently large $T/A_p$ the result collapsed back to standard diffusion.]

  %(b)
  For a driven particle,
  we ignore 
  the effects of temperature 
  in these simulations.  
  We note that even at $T/A_p = 6.0$ 
  the hopping rate
  is much less than the
  frequency of the applied drive.
  This can be seen in the time scale in Fig.~\ref{fig:brownian},
  where the average hopping rate is approximately
  every $15000\tau$,
  a value much larger than $T = 100\tau$.
  At sufficiently high temperatures,
  Brownian motion does affect 
  the formation of Shapiro steps
  and can be observed in experiments.
  %and could be included
  %to emulate noise seen in some 
  %How does Brownian motion affect
  %With driving force reproduce the paper figures...
  %%[there is no way I want to run this with python...]

@@

  A range of oscillation behaviors
  can be explored by varying the
  relative strength of the confining landscape
  and external driving force.
  For the single driven particle,
  the hopping patterns are typically characterized
  by $n_f$ the number of steps forward
  versus $n_b$ the number of steps backward within a single
  time period.
  The total displacement of $(n_f - n_b) \lambda$ %integer steps of
  is the net hop length.  
  %the substrate period $$ characterize
  In Fig.~\ref{fig:0},
  the particle moves forward through two minima ($n_f = 2$),
  and does not move backward a full minima ($n_b = 0$).  
  %such that the pattern
  %is characterized as $2(2,0)$.
  In order to achieve
  backwards hops,
  the driving parameters must have
  a ratio of $F^{ac}/F^{dc} > 1$ 
  and a difference $|F^{ac} - F^{dc}| > A_p$.
  %which can also produce large forward hops.
  %INSERT figure with a range of hopping patterns for a run
  The frequency must be sufficiently low so that 
  the applied force is large
  over a sustained time interval,
  allowing a particle to hop a substrate maxima.
  Experiments with single colloids \cite{Juniper2015} 
  show 
  hopping patterns with backward steps are more difficult
  to achieve than forward,
  with $n_f = 0$ to $6$ for $n_b = 0$,
  $n_f = 0$ to $5$ for $n_b = -1$,
  and
  $n_f = 2$ to $3$ for $n_b = -2$
  were realized 
  for a variety of applied forces parameters $F^{dc}$ and $F^{ac}$.
  {\bf Find the parameters
  that create hopping patterns similar to those in Ref.~\cite{Juniper2015}}.

  In Fig.~\ref{fig:hops}
  we show the effects of lowering the frequency
  of applied driving force,
  holding the remaining parameters fixed 
  to 
  $F^{dc}=0.1$, $F^{ac}=0.05$, and $A_p = 0.1$.
  We observe no backward steps 
  ($n_b = 0$) 
  across a broad range of frequencies.
  The number of forward steps 
  $n_f$ increases as frequency decreases.
  Low frequencies
  result in sustained positive or negative motion of a particle,
  where in Fig.~\ref{fig:hops}(e)
  the particle reaches the top edge of the system
  and wraps back to $y=0$.
  \begin{center}
    \begin{figure}[h!]
      \centering
      \includegraphics[width=\columnwidth]{{parameters_fig5}.pdf}
      \caption{
        Motion of a particle with the same values of $F^{dc} = 0.1$ and $F^{ac} = 0.05$ as Fig.~\ref{fig:1} and decreasing frequency as marked.
        In (e) the particle wraps the periodic boundary conditions.
      }
      \label{fig:hops}
    \end{figure}
  \end{center}
  %In Fig.~\ref{fig:hops}

  In Fig.~\ref{fig:hops_back}
  we fix $f=0.01$, $F^{dc}=0.1$, and and $A_p = 0.1$.
  We show the results for increasing $F^{ac} = 0.2, 0.3, 0.4$.
  %of the system for our original parameters.
  Here $n_b$ increases from $n_b = 0$ in (a) to
  $n_b = 2$ in (b) to $n_b = 4$ in (c).  
  \begin{center}
    \begin{figure}[h!]
      \centering
      \includegraphics[width=\columnwidth]{{parameters_fig6}.pdf}
      \caption{
        Motion of a particle with the same values of $F^{dc}$ and frequency as Fig.~\ref{fig:1} and increasing $F^{ac}$.
        (a) The particle moves forward six minima with no steps backward.
        (b) The particle moves forward eight minima with two steps backward.
        (c) The particle moves forward nine minima with four steps backward.
      }
      \label{fig:hops_back}
    \end{figure}
  \end{center}
  %In Fig.~\ref{fig:hops}

  Shapiro steps
%\item Frenkel-Kontorova and competing length scales for low temperature systems where thermal fluctuations are negligible
%  \item The Fokker-Planck Equation
%  \item Aubrey-Kontorova + commensurability
%  \item nanotribology
 %   kink motion
 %   Vanossi et al J.Phys.: Condens. Matter 19 (2007)
  %\item

@@

    \bibitem{numpy} Harris, C.R., Millman, K.J., van der Walt, S.J. et al. Array programming with NumPy. Nature {\bf 585}, 357 (2020). %DOI: 0.1038/s41586-020-2649-2. (Publisher link).
